{\bf {\Large Title....}}

### 2016-07-10 ident_manu.Rnw
working on p1 z1 eval

<<echo = F>>=
temp_coll <- par_txt(c('Tref(nospA+nospZ)_1', 'Tref(nospA+nospZ)_2', 'Tref(nospA+nospZ)_3', 'Tref(nospA+nospZ)_4', 'Tref(nospA+nospZ)_5', 'Tref(nospA+nospZ)_6', 'Tref(nospA+nospZ)_7', 'Tref(nospA+nospZ)_8'))

A comparison of average and median identifiability by parameter category and top parameters in each category suggested that individual parameters had large effects on $\gamma$ (\cref{fig:identbox}).  For example, a consistent increase in average $\gamma$ from 2 to 7 parameters in a combination for temperature was observed, whereas median identiability remained low until 6 parameter combinations were evaluated.  Further evaluation showed that identifiability was greatly affected by the inclusion of two parameters in a subset combination.  \Cref{fig:excltemp} shows the temperature collinearity ranges in detail for the parameter subsets in \cref{fig:identbox} with and without the inclusion of parameters.  Collinearity increases with more parameters included in a subset, although the increase varies depending on the specific parameter.  Exclusion of the parameters \Sexpr{temp_coll[2]} and \Sexpr{temp_coll[5]} showed that $\gamma$ remained well below the 10, 15 threshold for all parameters combinations.  Morever, inclusion of \Sexpr{temp_coll[1]}, \Sexpr{temp_coll[4]}, \Sexpr{temp_coll[7]}, and \Sexpr{temp_coll[8]} generally reduced collinearity relative to when the parameters were excluded.  Similar analyses identified parameters in other categories that had disproportionate effects on identifiability if included in a subset (see supplementary information).

@@

>>>>

<<echo = F>>=
temp_coll <- par_txt(c('Tref(nospA+nospZ)_1', 'Tref(nospA+nospZ)_2', 'Tref(nospA+nospZ)_3', 'Tref(nospA+nospZ)_4', 'Tref(nospA+nospZ)_5', 'Tref(nospA+nospZ)_6', 'Tref(nospA+nospZ)_7', 'Tref(nospA+nospZ)_8'))
@

A comparison of average and median identifiability by parameter category and top parameters in each category suggested that individual parameters had large effects on $\gamma$ (\cref{fig:identbox}).  For example, a consistent increase in average $\gamma$ from 2 to 7 parameters in a combination for temperature was observed, whereas median identiability remained low until 6 parameter combinations were evaluated.  Further evaluation showed that identifiability was greatly affected by the inclusion of one or two specific parameters in a subset combination.  \Cref{fig:excltemp} shows the temperature collinearity ranges in detail for the parameter subsets in \cref{fig:identbox} with and without the inclusion of parameters.  Collinearity increases with more parameters included in a subset, although the increase varies depending on the specific parameter.  Exclusion of the parameters \Sexpr{temp_coll[2]} and \Sexpr{temp_coll[5]} showed that $\gamma$ remained well below the 10, 15 threshold for all parameters combinations.  Morever, inclusion of \Sexpr{temp_coll[1]}, \Sexpr{temp_coll[4]}, \Sexpr{temp_coll[7]}, and \Sexpr{temp_coll[8]} generally reduced collinearity relative to when the parameters were excluded.  Similar analyses identified parameters in other categories that had disproportionate effects on identifiability if included in a subset (see supplementary information).

@@

% identifiability boxplot, p1, z1 only
<<p1z1identbox, fig.cap = 'Identifiability (as $\\gamma$, \\cref{gameq}) of parameter subsets for \\ac{do} using only subsets from the first phytoplankon group and first zooplankton group. Plots in (a) show identifiability for only the phytoplankton and zooplankton categories and (b) shows identifiability by selecting the top 1 through 5 parameters regardless of category. Lines represent identifiability ranges for the possible combinations given the number of parameters in the set.', fig.height = 10, fig.width = 4, echo = F, cache = TRUE, out.width = '0.6\\textwidth'>>=
data(p1z1cat_ident)
data(p1z1top_ident)

toplo1 <- p1z1cat_ident %>% 
  lapply(., function(x) dplyr::select(x, N, coll)) %>% 
  reshape2::melt(., id.var = c('N', 'coll')) %>% 
  rename(Category = L1) %>% 
  mutate(Category = factor(Category, 
    levels = c('Phytoplankton', 'Zooplankton'),
    labels = c('Phytoplankton', 'Zooplankton')
    )) %>% 
  filter(N <= 25) %>% # reduced for plot space
  group_by(N, Category) %>% 
  summarise(
    ave = mean(coll), 
    med = median(coll),
    min = min(coll), 
    max = max(coll)
  )

# identifiability top 1, 2, 3, 4, 5 all categories combined
toplo2 <-  reshape2::melt(p1z1top_ident, id.var = c('N', 'coll')) %>% 
  select(N, coll, L1) %>% 
  mutate(L1 = factor(L1, levels = paste0('top', 1:5), labels = paste0('Top ', 1:5))) %>% 
  rename(npercat = L1) %>% 
  group_by(N, npercat) %>% 
  summarise(
    ave = mean(coll), 
    med = median(coll),
    min = min(coll), 
    max = max(coll)
  )

p1 <- ggplot(toplo1, aes(x = N, group = N)) + 
  geom_errorbar(aes(ymin = min, ymax = max), width = 0, colour = 'darkgrey') + 
  geom_point(aes(y = ave, shape = 'Ave'), colour = 'black') + 
  geom_point(aes(y = med, shape = 'Med'), colour = 'black') + 
  facet_wrap(~ Category, ncol = 1, scales = 'free_y') +
  theme_minimal() + 
  theme(
    axis.line.x = element_line(), 
    axis.line.y = element_line(), 
    axis.title.x = element_blank(), 
    axis.title.y = element_blank()
  ) + 
  theme(legend.position = 'none') +
  ggtitle('(a) By parameter category')

grid.arrange(
  arrangeGrob(p1, p2, ncol = 1, heights = c(0.5, 1)),
  left = 'Identifiability', 
  bottom = 'Parameters in set',
  pleg, ncol = 2, widths = c(1, 0.1)
)

### 2016-07-10 ident_manu.tex
working on p1 z1 eval

\begin{singlespace}
\title{{\bf {\Large Title....}}}
\author{
  {\bf {\normalsize Marcus W. Beck$^1$, John C. Lehrter$^1$}}
  \\\\{\textit {\normalsize $^1$USEPA National Health and Environmental Effects Research Laboratory}}
  \\{\textit {\normalsize Gulf Ecology Division, 1 Sabine Island Drive, Gulf Breeze, FL 32561}}
	\\{\textit {\normalsize Phone: 850-934-2480, Fax: 850-934-2401}}
	\\{\textit {\normalsize Emails: \href{mailto:beck.marcus@epa.gov}{beck.marcus@epa.gov}, \href{mailto:lehrter.john@epa.gov}{lehrter.john@epa.gov}}}
  \vspace{1in} 
  \\ Version Date:   Sat Jul 9 15:31:45 2016 -0500
	}
\date{}
\maketitle
\end{singlespace}
\clearpage

@@

A comparison of average and median identifiability by parameter category and top parameters in each category suggested that individual parameters had large effects on $\gamma$ (\cref{fig:identbox}).  For example, a consistent increase in average $\gamma$ from 2 to 7 parameters in a combination for temperature was observed, whereas median identiability remained low until 6 parameter combinations were evaluated.  Further evaluation showed that identifiability was greatly affected by the inclusion of two parameters in a subset combination.  \Cref{fig:excltemp} shows the temperature collinearity ranges in detail for the parameter subsets in \cref{fig:identbox} with and without the inclusion of parameters.  Collinearity increases with more parameters included in a subset, although the increase varies depending on the specific parameter.  Exclusion of the parameters \textit{Tref(nospA+nospZ)$_{p2}$} and \textit{Tref(nospA+nospZ)$_{p5}$} showed that $\gamma$ remained well below the 10, 15 threshold for all parameters combinations.  Morever, inclusion of \textit{Tref(nospA+nospZ)$_{p1}$}, \textit{Tref(nospA+nospZ)$_{p4}$}, \textit{Tref(nospA+nospZ)$_{z1}$}, and \textit{Tref(nospA+nospZ)$_{z2}$} generally reduced collinearity relative to when the parameters were excluded.  Similar analyses identified parameters in other categories that had disproportionate effects on identifiability if included in a subset (see supplementary information).

@@

>>>>

\begin{singlespace}
\title{{\bf {\Large Title....}}}
\author{
  {\bf {\normalsize Marcus W. Beck$^1$, John C. Lehrter$^1$}}
  \\\\{\textit {\normalsize $^1$USEPA National Health and Environmental Effects Research Laboratory}}
  \\{\textit {\normalsize Gulf Ecology Division, 1 Sabine Island Drive, Gulf Breeze, FL 32561}}
	\\{\textit {\normalsize Phone: 850-934-2480, Fax: 850-934-2401}}
	\\{\textit {\normalsize Emails: \href{mailto:beck.marcus@epa.gov}{beck.marcus@epa.gov}, \href{mailto:lehrter.john@epa.gov}{lehrter.john@epa.gov}}}
  \vspace{1in} 
  \\ Version Date:   Sun Jul 10 14:28:00 2016 -0500
	}
\date{}
\maketitle
\end{singlespace}
\clearpage

@@

A comparison of average and median identifiability by parameter category and top parameters in each category suggested that individual parameters had large effects on $\gamma$ (\cref{fig:identbox}).  For example, a consistent increase in average $\gamma$ from 2 to 7 parameters in a combination for temperature was observed, whereas median identiability remained low until 6 parameter combinations were evaluated.  Further evaluation showed that identifiability was greatly affected by the inclusion of one or two specific parameters in a subset combination.  \Cref{fig:excltemp} shows the temperature collinearity ranges in detail for the parameter subsets in \cref{fig:identbox} with and without the inclusion of parameters.  Collinearity increases with more parameters included in a subset, although the increase varies depending on the specific parameter.  Exclusion of the parameters \textit{Tref(nospA+nospZ)$_{p2}$} and \textit{Tref(nospA+nospZ)$_{p5}$} showed that $\gamma$ remained well below the 10, 15 threshold for all parameters combinations.  Morever, inclusion of \textit{Tref(nospA+nospZ)$_{p1}$}, \textit{Tref(nospA+nospZ)$_{p4}$}, \textit{Tref(nospA+nospZ)$_{z1}$}, and \textit{Tref(nospA+nospZ)$_{z2}$} generally reduced collinearity relative to when the parameters were excluded.  Similar analyses identified parameters in other categories that had disproportionate effects on identifiability if included in a subset (see supplementary information).

@@

% identifiability boxplot, p1, z1 only
\begin{figure}[!ht]

{\centering \includegraphics[width=0.6\textwidth]{figs/p1z1identbox-1}

\caption[Identifiability (as ]{Identifiability (as $\gamma$, \cref{gameq}) of parameter subsets for \ac{do} using only subsets from the first phytoplankon group and first zooplankton group. Plots in (a) show identifiability for only the phytoplankton and zooplankton categories and (b) shows identifiability by selecting the top 1 through 5 parameters regardless of category. Lines represent identifiability ranges for the possible combinations given the number of parameters in the set.}\label{fig:p1z1identbox}
\end{figure}
